### 2011-12-01 ack.tex
daily commit
went to XeLaTeX

The subject of the first chapter was inspired by the mentoring of Jennifer Cole. Important contributions to this dissertation were made by Stephen Anderson, who graciously agreed to serve on my committee, Michael Wagner, who gave me a goal, and Morris Halle, who taught me to never apologize.

I would like to thank my fellow students at Penn, but especially my cohort, Toni Cook, Laurel MacKenzie, and Stefanie Brody. Elsewhere, I have been shown a great deal of kindness by so many, but especially Morgan Sonderregger and Maryam Bakht. Daniel Ezra Johnson fearlessly proofread (\emph{proofreaded}?) the entire document. Among non-linguists, my good friend Carly Fisher stands out for her unflagging support.

>>>>

The subject of the first chapter was inspired by the mentoring of Jennifer Cole. Important contributions to this dissertation were made by Stephen Anderson, who graciously agreed to serve on my committee, Michael Wagner, who gave me a goal to work towards, and Morris Halle, who taught me to never apologize.

I would like to thank my fellow students at Penn, but especially my cohort, Toni Cook, Laurel MacKenzie, and Stefanie Brody. Elsewhere, I have been shown a great deal of kindness by so many, but especially Morgan Sonderregger and Maryam Bakht. Daniel Ezra Johnson fearlessly proofread (\emph{proofreaded}?) the entire document. Among non-linguists, my good friend Carly Fisher stands out for her unflagging support. Among parents, mine stand out for having more faith in their son than he could ever merit.

### 2011-12-01 clusters.tex
went to XeLaTeX

@@

\section{The null hypothesis}

@@

\ex Russian reflexives \citep[after][]{Jakobson1932}: \\
\begin{tabular}{l l l l} %\toprule
   &  infinitive & imperative \\ %\midrule
a. & [\textprimstress sl\textceltpal av\textceltpal its\textschwa]         & [\textprimstress slaf\textceltpal s\textschwa]            & `be glorious'    \\
   & [u\textprimstress pramits\textschwa]         & [u\textprimstress pram\textceltpal s\textschwa]          & `be stubborn'    \\
b. & [\textprimstress kras\textceltpal its\textschwa]         & [\textprimstress kras\textceltpal s\textschwa]           & `put on makeup'  \\
   & [\textprimstress\textyogh arits\textschwa]       & [\textprimstress\textyogh ar\textceltpal s\textschwa]         & `roast'          \\ 
c. & [\textprimstress z\textschwa byts\textschwa] & [\textprimstress z\textschwa but\textceltpal s\textschwa] & `forget' \\ %\bottomrule
%   & ab\'utsa      & ab\'ujsa     & `put on shoes'   \\
\end{tabular} \xe

@@

\begin{table}
\centering
\begin{tabular}{l r l r r}
\toprule
harmonic      & \#   & disharmonic & \#   \\
\midrule
\buf[pemez]   & $30$ & [pemaz]     & $2$  \\
\buf[teriz]   & $28$ & [ter\i z]   & $3$  \\
\buf[tokaz]   & $26$ & [tokez]     & $6$  \\
\buf[tipez]   & $24$ & [tipaz]     & $8$  \\
\buf[ter\"uz] & $19$ & [teruz]     & $13$ \\
\bottomrule
\end{tabular}
\caption{this is at test \citet[][314]{Zimmer1969}}
\label{backharm}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{l r l r}
\toprule
harmonic & \# & disharmonic & \# \\
\midrule
\buf[tafuz] & $21$ & [taf\i z] & $11$ \\
\buf[pamuz] & $17$ & [pam\i z] & $15$ \\
\buf[tapuz] & $17$ & [tap\i z] & $15$ \\
\buf[mavuz] & $16$ & [mav\i z] & $16$ \\
\buf[tabuz] & $16$ & [tab\i z] & $16$ \\
\bottomrule
\end{tabular}
\caption{this is at test \citet[][314]{Zimmer1969}}
\label{labcons}
\end{table}

Here is it clear that the preferences, while going in the expected direction, are far smaller ($\gamma = 0.088$). Further, only one of five pairs, \emph{tafuz} $\sim$ \emph{taf\i z}, matches the stronger preferences seen with backness harmony. It might be possible to though any failure to find significance here should surely be attributed to insufficient statistical power, not evidence for the null hypothesis.

@@

>>>>

ontogeny reveals ontology

\chapter{Structural and accidental phonotactic gaps in the lexicon}

Some (admittedly similar)

Some evidence that this is active comes from a study by \citet[]{Wright1975}. \citeauthor{Wright1975} taught several members of a ``neighborhood gang'' a few words from an artificial language, and then asked them to repeat the words to each other in a game of ``telephone''. Crucially

A particularly

\ex Artificial language repetitions \citep[from][]{Wright1975}: \\
\begin{tabular}{l l l l l l} %\toprule
%a. & [go\textupsilon np] & $>$ & [gu\lm mp] \\
%[g\textturnv np]  
%b. & [\dh \textturnv\textipa{N}d] & $>$ & [\dh \textopeno\textipa{N}g\textschwa] \\ % $>$ [t\textopeno\textipa{N}g\textschwa] 
%c. & [\textdyoghlig umg] & $>$ & [\textdyoghlig u\textipa{N}g\textschwa] \\
\end{tabular} \xe

\noindent
While a number of other adaptations there 
[np] becomes [mp],

%[\textipa{N}d] becomes [nd], and [mg] becomes [\textipa{N}g].

[ɳd]

t
If this task is viewed as something like loanword adaptation, then there are certainly good reasons to think that extragrammatical pressures \citep{Dupoux1999,Ussishkin2003,Peperkamp2008} could be responsible for what is observed. That said, it is certainly noteable that

\footnote{In this latter view, it is interesting that the (\lastx c) final nasal-[g] cluster is preserved. In standard }

\citep{Schleef2011}

%[\textipa{N}g] is certainly

though it can be found in the speech fo

There is good phonological eivd

In this latter view, it is interesting that the finIn this latter view, it is interesting that the finIn this latter view, it is interesting that the final [g] is preserved.

As \citeauthor{Wright1975} notes, it is particularly interesting that

It is particularly interesting that 
%included a stimulus with [\textipa{N}] as a control, since

There is a lengthy literature arguing for a phonotactic component to speakers' phonological knowledge. The fundamental argument pursued in this chapter is that many of these studies are misguided, and fail to take into account a powerful null hypothesis.

@@

\section{Preliminaries}

\subsection{Some definitions}

\subsection{The null hypothesis}

\subsubsection{History of the null}

@@

\ex Russian reflexives \citep[after][]{Jakobson1932}: \\
\begin{tabular}{l l l l} %\toprule
   &  infinitive & imperative \\ %\midrule
a. & [slav\textceltpal its\textschwa]         & [slaf\textceltpal s\textschwa]            & `be glorious'    \\
   & [pramits\textschwa]         & [upram\textceltpal s\textschwa]          & `be stubborn'    \\
b. & [kras\textceltpal its\textschwa]         & [kras\textceltpal s\textschwa]           & `put on makeup'  \\
   & [\textyogh arits\textschwa]       & [\textyogh ar\textceltpal s\textschwa]         & `roast'          \\ 
c. & [z\textschwa byts\textschwa] & [z\textschwa but\textceltpal s\textschwa] & `forget' \\ %\bottomrule
%   & ab\'utsa      & ab\'ujsa     & `put on shoes'   \\
\end{tabular} \xe

@@

\begin{table}
\centering
\begin{tabular}{l r l r r}
\toprule
harmonic      & \#   & disharmonic & \#   \\
\midrule
\emph{pemez}  & $30$  & \emph{pemaz}     & $2$  \\
\emph{teriz}   & $28$ & \emph{ter\i z}   & $3$  \\
\emph{tokaz}   & $26$ & \emph{tokez}     & $6$  \\
\emph{tipez}   & $24$ & \emph{tipaz}     & $8$  \\
\emph{ter\"uz} & $19$ & \emph{teruz}     & $13$ \\
\bottomrule
\end{tabular}
\caption{this is at test \citet[][314]{Zimmer1969}}
\label{backharm}
\end{table}
% c = 127, d = 32, p = 5.233e-29

@@

\begin{table}
\centering
\begin{tabular}{l r l r}
\toprule
harmonic & \# & disharmonic & \# \\
\midrule
\emph{tafuz} & $21$ & \emph{taf\i z} & $11$ \\
\emph{pamuz} & $17$ & \emph{pam\i z} & $15$ \\
\emph{tapuz} & $17$ & \emph{tap\i z} & $15$ \\
\emph{mavuz} & $16$ & \emph{mav\i z} & $16$ \\
\emph{tabuz} & $16$ & \emph{tab\i z} & $16$ \\
\bottomrule
\end{tabular}
\caption{this is at test \citet[][314]{Zimmer1969}}
\label{labcons}
\end{table}
% c = 87, d = 73, p = 0.101

Here is it clear that the preferences, while going in the expected direction, are far smaller ($\gamma = 0.088$). There are ties for two of the lexical items, and only one of the five pairs, \emph{tafuz} $\sim$ \emph{taf\i z}, matches the stronger preferences seen with backness harmony. If we remove this pair, $\gamma = 0.032$.  It might be possible to though any failure to find significance here should surely be attributed to insufficient statistical power, not evidence for the null hypothesis.

@@

Degemination

\citet[][20]{Harris1994}
